Dynein walks like an Imperial AT-ST

### 2018-08-23 papers/paper/paper.tex
minor commit

  \section*{Fitting $k_b$ and $k_{ub}$}
  To fit the binding and unbinding rate constants $k^0_b$ and $k^0_{ub}$, a simple theoretical model for stepping was used. First, it is assumed that the unbinding rate of an MTBD does not depend on the binding state of the other MTBD. Then the dissociation rate of the whole complex from the microtubule, $k_{dis}$, is estimated as $k_{dis} = P(ob)*k_{ub} = \frac{<t_{ob}}{t_{step}} * \frac{1}{<t_{bb}}$, where $P(ob)$ is the probability of a dynein complex being in the onebound state, $<t_{ob}>$ and $<t_{bb}>$ are the expected durations for a onebound and bothbound state, and $<t_{step}> = <t_{ob}> + <t_{bb}>$ is the expected step duration. Plugging in the last definition yields $k_{dis} = \frac{<t_{step}> - <t_{bb}}{<t_{step}><t_{bb}>}$. Introducing a new variable $<t_{run}>$, the average run length of in vivo dynein, and using the relation $<t_{run}> = k_{dis}^{-1}$, a new relation is found for bothbound time: $<t_{bb}> = \frac{<t_{run}><t_{step}>}{<t_{run}>+<t_{step}>}$. Using the definition of $<t_{step}>$ a similar relation is found for onebound time: $<t_{ob}> = \frac{<t_{step}>^2}{<t_{step}>+<t_{run}>}$. Finally, using the relation $<t_{step}> = \frac{v}{<L_{step}>}$ for dynein velocity $v$ and expected step length $<L_{step}>$, the following equations are found for onebound and bothbound time in terms of experimental observables of velocity, run time and step length:

  \begin{align}
    <t_{ob}> &= \frac{v^2}{L_{step}^2\left(v/L_{step}+<t_{run}>\right)}\\
    <t_{bb}> &= \frac{v<t_{run}>}{L_{step}\left(<t_{run}>+v/L_{step}\right)}
  \end{align}

>>>>

  \section*{Fitting $k_b$ and $k_{ub}$}
  To fit the binding and unbinding rate constants $k^0_b$ and $k^0_{ub}$, a simple theoretical model for stepping was used. First, it is assumed that the unbinding rate of an MTBD does not depend on the binding state of the other MTBD. Then the dissociation rate of the whole complex from the microtubule, $k_{dis}$, is estimated as $k_{dis} = P(ob)*k_{ub} = \frac{\bar{t}_{ob}}{\bar{t}_{step}} * \frac{1}{\bar{t}_{bb}}$, where $P(ob)$ is the probability of a dynein complex being in the onebound state, $\bar{t}_{ob}$ and $\bar{t}_{bb}$ are the expected durations for a onebound and bothbound state, and $\bar{t}_{step} = \bar{t}_{ob} + \bar{t}_{bb}$ is the expected step duration. Plugging in the last definition yields $k_{dis} = \frac{\bar{t}_{step} - \bar{t}_{bb}}{\bar{t}_{step}\bar{t}_{bb}}$. Introducing a new variable $\bar{t}_{run}$, the average run length of in vivo dynein, and using the relation $\bar{t}_{run} = k_{dis}^{-1}$, a new relation is found for bothbound time: $\bar{t}_{bb} = \frac{\bar{t}_{run}\bar{t}_{step}}{\bar{t}_{run}+\bar{t}_{step}}$. Using the definition of $\bar{t}_{step}$ a similar relation is found for onebound time: $\bar{t}_{ob} = \frac{\bar{t}_{step}^2}{\bar{t}_{step}+\bar{t}_{run}}$. Finally, using the relation $\bar{t}_{step} = \frac{v}{L_{step}}$ for dynein velocity $v$ and expected step length $\bar{L}_{step}$, the following equations are found for onebound and bothbound time in terms of experimental observables of velocity, run time and step length:

  \begin{align}
    \bar{t}_{ob} &= \frac{v^2}{\bar{L}_{step}^2\left(v/\bar{L}_{step}+\bar{t}_{run}\right)}\\
    \bar{t}_{bb} &= \frac{v\bar{t}_{run}}{\bar{L}_{step}\left(\bar{t}_{run}+v/\bar{L}_{step}\right)}
  \end{align}
